---
title: "IP_week13"
author: "Stephen Njuguna"
date: "1/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Customer Groups

## Defining the question 
Learn the customer’s behavior and characteristics  and group them. 

## Defining the metric for success
Being able to sucessfully cluster the customers 

## Understanding the context
Understanding consumer behavior is a vital aspect of marketing. Consumer behavior is the study of how people make decisions about what they buy, want, need, or act in regards to a product, service, or company. It also helps companies identify opportunities that are not currently met.

## Experimental design
 * Problem Definition
 * Data Sourcing
 * Check the Data
 * Perform Data Cleaning
 * Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
 * Implement the Solution
 * Challenge the Solution


## Read Our Dataset

```{r}
#Reading the Dataset and preveiwing dataset  

customer <- read.csv('http://bit.ly/EcommerceCustomersDataset')

head(customer)
```
```{r}
#Checking the data types 
str(customer)
```

```{r}
#Checking data dimension 
dim(customer)
```
## Data Cleaning 

```{r}
#Checking for missing values 
colSums(is.na(customer))
```

```{r}
#Dealing with the missing values  
customer <- na.omit(customer)

#Dropping all the missing value because they are a very few caparisoning to
# the number of rows we have 
```

```{r}
#Checking for duplicates and dealing with duplicates if any 

customer <- unique(customer)
```

```{r}
#Checking for outliers 
#slecting only numeric columns 
library(dplyr)
numeric <- select_if(customer, is.numeric)

#ploting box plots 
invisible(lapply(1:ncol(numeric), function(i) boxplot(numeric[, i])))

```

## Exploratory Data Analysis

### Univeriate Analysis

```{r}
#Check statistical summary of data 
summary(numeric)
```


```{r}
#Plotting Visitor ype
v_type <- table(customer$VisitorType)
barplot(v_type)
```

Most of the customer are the returning_visitors.

```{r}
#Plotting month
month <- table(customer$Month)
barplot(month)
```

Most customers visit the e-commerce site on the month of May followed by November.
The month with the least visits in February 


```{r}
#Plotting the customers Bounce rate 
hist(numeric$BounceRates)
```
Most of the the visiting clients exit  without triggering any other requests 
to the analytics server.

```{r}
#Plotting the page value 
hist(numeric$PageValues)
```

Most customers visit 0-10 pages before completing e-commerce transaction.


```{r}
#Plotting the special day column 
hist(numeric$SpecialDay)
```

Most people visit before or after the special day.

## Biavariate Analysis

```{r}
#Plotting a correlation plot 
corr<-cor(numeric)
corrplot::corrplot(corr, method="number")

```



```{r}
#Plotting a scatter plot between bounce and exit rate 
bounce <- numeric$BounceRates
exit <- numeric$ExitRates
plot(bounce, exit, xlab="bounce", ylab="Exit")

```


There is strong correlation between bounce and exit rate

```{r}
#Plotting scatter plot between page value and special day
value <- numeric$PageValues
day<- numeric$SpecialDay
plot(value, day, xlab="Page value", ylab="Special Day")


```

There is a strong correctional between page value and special day.


## Multivariate Analysis

```{r}
#Label econding categorical columns to numeric 
customer$VisitorType <- as.numeric(factor(customer$VisitorType))
customer$Weekend <- as.numeric(factor(customer$Weekend))
customer$Region <- as.numeric(factor(customer$Region))
customer$Revenue <- as.numeric(factor(customer$Revenue))
customer$Month <- as.numeric(factor(customer$Month))

```


```{r}
custm <- customer[c(-18)]
#Performing dimension reduction using PCA
dim_customer <- prcomp(custm,scale. = FALSE)

summary(dim_customer)
```


## Modeling 

### Heirarchical clustering 

```{r}
#Scale the dataset 
scaled.custm <- scale(custm)
```

```{r}
## Calculate the (Euclidean) distances
hist.custm <- dist(scaled.custm)
```

```{r}
## Create a hierarchical clustering model
clust.custm <- hclust(hist.custm, method = 'complete')
```

```{r}
#Plot (Dendrogram) the clusters to get height 
plot(clust.custm)
```
```{r}
## Cut tree so that it has 2 clusters:
custm.clusters <- cutree(clust.custm, k = 2)
```

```{r}
# Compare heirarchical cluster to actual clusters
table(custm.clusters)
table(customer$Revenue)
```

Hierarchical cluster ,groups 1's as 12196 compared to the actual of 10291 and group 2's 
as 3 compared to the actual group of 1908


### k-means clustering

```{r}
#Normalization of the data
normal <- function(x) (
  return( ((x - min(x)) /(max(x)-min(x))) )
)
normal(1:18)
nom.custm<- as.data.frame(lapply(customer[,-18], normal))
```


```{r}
# Create a k-means model on 
custm.km <- kmeans(nom.custm, centers = 2, nstart = 20)
```


```{r}
#Plotting the clusters 
plot(custm[c(2,9)], col = custm.km$cluster)
```
```{r}
# Compare k Mean cluster to actual clusters
table(custm.km$cluster)
table(customer$Revenue)
```


K Mean cluster ,groups 1's as 2856 compared to the actual of 10291 and group 2's 
as 9343 compared to the actual group of 1908



### Comparisons between K-Means clustering vs Hierarchical

```{r}
# Compare hierarchical clustering to k-means
table(custm.clusters)
table(custm.km$cluster)
```


## Conclusion 

K mean clustering performance much better compared to Hierarchical clustering.

  * K mean cluster works better than hierarchical clustering when it come to large 
datasets , which in our case we had a large dataset.
  * K Means clustering needed advance knowledge of  no. of clusters one 
  want to divide your data compared to hierarchical cluster which finds
  appropriate by interpreting the dendrogram. In our case we have knowledge of 
  the number of clusters.
  * K mean clustering is very sensitive to outliers because when you have 
  outliers, this can affect the average calculation of the whole cluster.
  







